
\documentclass[usletter, 10pt, conference]{ieeeconf}
\newcommand{\mbm}[1]{\mbox{\boldmath $#1$}}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}
\usepackage{url}

\usepackage[ruled]{algorithm2e}
\usepackage{subfigure}
\usepackage{graphicx,color,psfrag}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bigdelim}
\usepackage{dsfont}
\usepackage{color, soul}
%\usepackage[section]{placeins}
%\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

\overrideIEEEmargins
\title{The Autonomous Picking \& Palletizing (APPLE) Robot:\\ A Research Platform for
  Intralogistics Applications} 

% Multiple authors
\author{ \authorblockN{Robert Krug\superscript{*}, Todor Stoyanov\superscript{*}, Vinicio
    Tincani\superscript{\ddag}, Henrik Andreasson\superscript{*},\\ Rafael Mosberger\superscript{*},
    Gualtiero Fantoni\superscript{\ddag}, Achim J. Lilienthal\superscript{*} and Antonio
    Bicchi\superscript{\ddag}}
 %\authorblockA{\superscript{*}AASS Research Center, {\"O}rebro University, Sweden}
}

\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}
%
\blfootnote{\hspace{-4.5mm} \superscript{*} AASS Research Center; {\"O}rebro University; Studentgatan 1, 70182 {\"O}rebro, Sweden.\\
  \superscript{\ddag} Interdepart. Research Center ``E. Piaggio''; University of Pisa, Via Diotisalvi 2, 56100 Pisa, Italy.}
%
\begin{abstract}
  In this work we present a research platform for fully autonomous commissioning tasks in
  intralogistics settings. The robot comprises a nonholonomic mobile base and a manipulation system
  consisting of a lightweight arm and an under-actuated gripper with active surfaces. The platform
  is capable of autonomously picking up pallets and loading them with unstructured goods in a manner
  which is safe for human workers sharing the environment. Target object handling is accomplished
  via a novel, redundant grasp representation which allows for redundancy in the gripper pose
  placement. This redundancy is exploited by an optimization-based control system which generates
  reactive manipulator motions on-the-fly without the delays occurring in sense-plan-act
  architectures.
\end{abstract}
%
\input{Introduction} 
%
\input{AGV}
%
\input{Grasping}
%
\input{Evaluation}
%
\input{Discussion}

%
\section*{Acknowledgments}
%
The authors would like to thank Per Sporrong, Bo-Lennart Silfverdal, Bengt {\AA}sberg and Joakim
Larsson at {\"O}rebro University for their engineering support.
%
\bibliographystyle{IEEEtran}
\bibliography{References}

% \newpage
% REMARKS:
% \begin{itemize}
% \item cite the books stating that shifting of initial states is not a problem
% \end{itemize}

\end{document}



