\section{Introduction}
\label{sec:intro}
%
The increasing need for fast and flexible commissioning (i. e., order picking and collection of
unstructured goods from storage compartments in warehouses) in logistic scenarios has created
substantial interest for autonomous robotic solutions. This was also evidenced by a recent BBC
investigation into a UK-based Amazon warehouse, which highlighted that the dull and strenuous nature
of commissioning could cause mental and physical illness in human workers. Amazon themselves took
action by organizing their first Picking Challenge at ICRA 2015.

The key obstacle for many application scenarios is the autonomous grasping in uncer- tain real-world
environments. Currently, despite of a large research effort, no commer- cially viable solution is
available for this problem. State of the art autonomous grasping systems~\cite{Bere07, Srin10,
  Krug14a} commonly employ sampling based planners~\cite{Lava06} to generate online reach-to-grasp
motion plans for offline planned grasps which are stored in a database.  During the execution phase,
such approaches necessitate many futile motion planning attempts which often incurs significant time
delays mainly due to the frequent colli- sion checks which are necessary to avoid the robot coming
in contact with itself or the environment.  For APPLE, we adopted a real-time reactive control
approach for manipulator mo- tion generation which allows to exploit redundancy, opposed to the
commonly used sense-plan-act architectures which constrain all manipulator DoF. The main idea is to
formulate a hierarchical set of tasks~\cite{Sams91} such as “move end-effector on this plane” or
“avoid joint limits” and to compute controls such that tasks of lower priorities are exe- cuted in
the null-space of higher ranked tasks~\cite{Sici91, Khat04, Sent10}.
